Report

### 2020-10-05 report.Rmd
Fix regression weigth + plot of prediction + data

---
title: "Report"
author: "Alain Danet"
output: html_document
---

@@

```{r p-bivar, cache = TRUE, fig.cap = bivar_cap, fig.height = 10}

cowplot::plot_grid(
  cowplot::plot_grid(plotlist = net_dyn_lm_plot$plot[1:4], ncol = 2),
  cowplot::plot_grid(plotlist = filter(net_dyn_lm_plot, group == "big")$plot[1:4], ncol = 2),
  ncol = 1, 
  axis = "rlbt",
  align = "hv",
  label_y = 1.01,
  label_x = .40,
  labels = c("Little community", "Big community")
)

@@

log_bm_min_max <- map_dbl(c(min, max),
  ~.x(data_decrease_increase$log_bm, na.rm = TRUE))
nb_year_min_max <- map_dbl(c(min, max),
  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
temporal_dynamics_plot$plot %<>%
  map(., ~ .x + lims(y = log_bm_min_max, x = nb_year_min_max))

temporal_dynamics_plot %>%
  filter(variable == "bm_std", station %in% st_decrease_increase_rigal$station) %>%
  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal$station)
```

@@

bm_min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase$biomass, na.rm = TRUE))
nb_year_min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
temporal_dynamics_plot[temporal_dynamics_plot$variable == "biomass",]$plot %<>%
  map(., ~ .x + lims(y = bm_min_max, x = nb_year_min_max))

@@

p_rigal_decrease_increase_slope_st <- 
  st_decrease_increase_rigal_biomass %>%
  left_join(biomass_group, by = "station") %>%
  ggplot(aes(y = linear_slope, x = value, color = shape_class)) +
  geom_point() +
  facet_wrap(~variable)
p_rigal_decrease_increase_slope_st
```

@@

```{r}
rigal_biomass_coeff_dynamics <- st_decrease_increase_rigal_biomass %>%
  select(station, linear_slope, strd_error) %>%
  left_join(temporal_dynamics_coef, by = "station") %>%
  filter(!coeff %in% get_biomass_var(), term == "slope") %>%
  select(station, coeff, estimate, std.error, linear_slope, bm_std_error = strd_error) %>%
  mutate(reg_weight = (abs(estimate / std.error) + abs(linear_slope / bm_std_error))/2)
rigal_biomass_coeff_dynamics %>%
  ggplot(aes(x = reg_weight)) +
  geom_histogram() +
  facet_wrap(~coeff)

rigal_biomass_coeff_dynamics %>%
  ggplot(aes(x = linear_slope, y = estimate, size = reg_weight, weight = reg_weight)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~coeff, scales = "free_y")
rigal_biomass_coeff_dynamics %>%
  ggplot(aes(x = linear_slope, y = estimate, size = reg_weight)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~coeff, scales = "free_y")
```

@@

```{r}
##Summary of group 
biomass_group %>%
  filter(group_type == "median") %>%
  ggplot(aes(x = bm)) +
  geom_histogram() +
  facet_wrap(bm_var~summary_type, scales = "free_x")

group_results <- 
  rigal_biomass_coeff_dynamics %>%
  left_join(biomass_group, by = "station") %>% 
  filter(group_type == "median", bm_var == "bm_std")

@@

```{r}
group_results_stream_size <- 
  group_results %>%
  left_join(
    filter(stream_group, group_type == "median") %>%
      rename(stream_group = group) %>% select(-group_type)
    , by = "station")

group_results_stream_size %>%
  filter(summary_type == "first_3_year", linear_slope < 8) %>%
  ggplot(aes(x = linear_slope, y = estimate, color = protocol_type, size = reg_weight, weight = reg_weight)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~coeff, scales = "free_y") +
  labs(title = "Group as protocol type")

group_results_stream_size %>%
  filter(summary_type == "first_3_year", linear_slope < 8) %>%
  ggplot(aes(x = linear_slope, y = estimate, color = protocol_type, size = reg_weight, weight = reg_weight)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~coeff, scales = "free_y") +
  labs(title = "Group as mean river size")

group_results_stream_size %>%
  filter(summary_type == "first_3_year", linear_slope < 8) %>%
  ggplot(aes(x = linear_slope, y = estimate, color = group, size = reg_weight, weight = reg_weight)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~coeff, scales = "free_y") +
  labs(title = "Group as mean river size")

group_results_stream_size %>%
  filter(summary_type == "median", linear_slope < 8) %>%
  ggplot(aes(x = linear_slope, y = estimate, color = group, size = reg_weight, weight = reg_weight)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~coeff, scales = "free_y") +
  labs(title = "Group as mean biomass")
```

@@

bm_net_group %>%
  filter(!is.na(protocol_type)) %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
  geom_point() +
  scale_color_viridis() +
  #geom_smooth(method = "lm") +
  facet_grid(variable~protocol_type, scales = "free") +
  labs(title = "Group as mean biomass")

@@

```{r, eval = FALSE}
model_int <- compute_my_lm_vs_net_model(bm_net_group, var_to_group = c("variable"))
model_vif <- get_vif(model_int, model_cols = c("mod3", "mod5",
    "mod6", "mod8", "mod9"))
model_vif %>%
  ggplot(aes(y = vif, x = term)) +
  geom_hline(yintercept = 10) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(model_type~variable)
```

@@

```{r}
model_by_protocol <- compute_my_lm_vs_net_model(
  filter(bm_net_group, !is.na(protocol_type)),
  var_to_group = c("variable", "protocol_type"),
  #var_to_scale = c("log_bm") 
)
model_var <- tidyselect::vars_select(names(model_by_protocol), starts_with("mod"))
model_vif <- get_vif(model_by_protocol,
  model_cols = model_var)
protocol_vec <- model_vif$protocol_type %>% unique
p_vif_protocol <- map(protocol_vec, function (x) {
  model_vif %>%
    filter(protocol_type == x) %>%
    ggplot(aes(y= vif, x = term)) +
    geom_hline(yintercept = 10) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = paste0("Protocol type: ", x)) +
    facet_grid(model_type~variable, scales = "free_y")
  })
p_vif_protocol[[1]]
p_vif_protocol[[2]]
```
```{r}
bm_net_group %>%
  filter(variable == "connectance") %>%
  ggplot(aes(x = bm_slope, y = bm)) +
  geom_point()

@@

```{r, eval = FALSE}
res_mod <- model_by_protocol %>%
  filter(protocol_type == "complete") %>%
  select(-data) %>%
  pivot_longer(cols = c(mod1:last_col()),
    names_to = "model", values_to = "model_obj") %>%
  mutate(
    resume = map(model_obj, summary),
    anova = map(model_obj, anova)
  )
```

```{r, eval = FALSE}
filter(res_mod, model == "mod_inc_bm")[["resume"]]
filter(res_mod, model == "mod_inc_bm")[["anova"]]

filter(res_mod, model == "mod_bm_inc")[["resume"]]
filter(res_mod, model == "mod_bm_inc")[["anova"]]
```

```{r, eval = FALSE}
pred <- res_mod %>%
  filter(model == "mod4") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
plot_grid(plotlist = pred$plot)
```

```{r, eval = FALSE}
res_mod7 %<>%
  mutate(
    pred7 = map(mod7, ~ggpredict(.x,
	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]", "inc_f"))),
    pred7_df = map(pred7, as_tibble),
    plot = map(pred7, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred7, ~plot(.x, add.data = TRUE)),
    myplot = map2(pred7, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )

#plot_final_model(model_int$pred5[[1]], model_int$data[[1]])
plot_grid(plotlist = res_mod7$plot, labels = res_mod7$variable)
plot_grid(plotlist = res_mod7$plot_data, labels = res_mod7$variable)

test <- model_int$data[[1]]
res_mod7$pred7_df[[1]]
test %>%
  ggplot(aes(x = bm_slope, y = linear_slope, weight = reg_weight, size = reg_weight)) +
  geom_smooth(method = "lm") +
  geom_point()

#pred_test <-
  #model_int$pred5_df[[1]] %>%
  #as_tibble %>%
  #rename(increasing = group, group = facet) %>%
  #filter(increasing == FALSE & x < 0 | increasing == TRUE & x > 0)

#p <- ggplot(pred_test, aes(x = x , y = predicted, color = group)) +
  #geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha =
    #.1) +
  #geom_line() +
  #geom_point(data = rename(test,
      #predicted = linear_slope, x = bm_slope),
    #aes(x = x, y = predicted),
    #inherit.aes = FALSE)
```

@@

```{r}
loadd(log_bm_net_group)
model_log <- compute_my_lm_vs_net_model(
  log_bm_net_group, var_to_group = c("variable"),
)

model_var <- tidyselect::vars_select(names(model_by_protocol), starts_with("mod"))
model_log_vif <- get_vif(model_log, model_cols = model_var)

model_log_vif %>%
  ggplot(aes(y= vif, x = term)) +
  geom_hline(yintercept = 10) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(model_type~variable)
```

```{r}
model_by_protocol <- compute_my_lm_vs_net_model(
  filter(log_bm_net_group, !is.na(protocol_type)),
  var_to_group = c("variable", "protocol_type")
)

model_var <- tidyselect::vars_select(names(model_by_protocol), starts_with("mod"))
model_vif <- get_vif(model_by_protocol,
  model_cols = model_var)

protocol_vec <- model_vif$protocol_type %>% unique
p_vif_protocol <- map(protocol_vec, function (x) {
  model_vif %>%
    filter(protocol_type == x) %>%
    ggplot(aes(y= vif, x = term)) +
    geom_hline(yintercept = 10) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = paste0("Protocol type: ", x)) +
    facet_grid(model_type~variable, scales = "free_y")
  })
p_vif_protocol[[1]]
p_vif_protocol[[2]]
```

```{r}
res_mod <- model_by_protocol %>%
  filter(protocol_type == "complete") %>%
  select(-data) %>%
  pivot_longer(cols = all_of(model_var),
    names_to = "model", values_to = "model_obj") %>%
  mutate(
    resume = map(model_obj, summary),
    anova = map(model_obj, anova)
  )
```

```{r}
filter(res_mod, model == "mod_inc_log_bm")[["resume"]]
filter(res_mod, model == "mod_inc_log_bm")[["anova"]]
```

```{r}
filter(res_mod, model == "mod_log_bm_inc")[["resume"]]
filter(res_mod, model == "mod_log_bm_inc")[["anova"]]
```

```{r, eval = FALSE}
pred <- res_mod %>%
  filter(model == "mod4") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
  )
plot_grid(plotlist = pred$plot)
```

>>>>

---
title: "Report"
author: "Alain Danet"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    math: katex
---

@@

```{r p-bivar, cache = TRUE, fig.cap = bivar_cap, fig.height = 10}
cowplot::plot_grid(
  cowplot::plot_grid(plotlist = net_dyn_lm_plot$plot[1:4], ncol = 2),
  cowplot::plot_grid(plotlist = filter(net_dyn_lm_plot, group == "big")$plot[1:4], ncol = 2),
  ncol = 1, 
  axis = "rlbt",
  align = "hv",
  label_y = 1.01,
  label_x = .40,
  labels = c("Little community", "Big community")
)

@@

log_bm_min_max <- map_dbl(c(min, max),
  ~.x(data_decrease_increase$log_bm_std, na.rm = TRUE))
nb_year_min_max <- map_dbl(c(min, max),
  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
temporal_dynamics_plot$plot %<>%
  map(., ~ .x + lims(y = log_bm_min_max, x = nb_year_min_max))

temporal_dynamics_plot %>%
  filter(variable == "log_bm_std", station %in% st_decrease_increase_rigal$station) %>%
  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal$station)
```

@@

bm_min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase$bm_std, na.rm = TRUE))
nb_year_min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
temporal_dynamics_plot[temporal_dynamics_plot$variable == "bm_std",]$plot %<>%
  map(., ~ .x + lims(y = bm_min_max, x = nb_year_min_max))

@@

p_rigal_decrease_increase_slope_st <- 
  st_decrease_increase_rigal_biomass %>%
  left_join(biomass_group, by = "station") %>%
  ggplot(aes(y = linear_slope, x = bm_slope, color = shape_class)) +
  geom_point() +
  facet_wrap(~variable)
p_rigal_decrease_increase_slope_st
```

@@

```{r}
loadd(bm_net_group, log_bm_net_group, bm_vs_net_trends)
bm_vs_net_trends %>%
  ggplot(aes(x = reg_weight)) +
  geom_histogram() +
  facet_wrap(~variable)

bm_net_group %>%
  ggplot(aes(x = bm_slope, y = linear_slope, size = reg_weight, weight = reg_weight, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_vline(xintercept = 0, color = "red") +
  geom_smooth() +
  facet_wrap(~variable, scales = "free_y") +
  labs(x = "Biomass trend (g.m-1.y-1)", y = "Network trend (U.y-1)")

log_bm_net_group %>%
  ggplot(aes(x = bm_slope, y = linear_slope, size = reg_weight, weight = reg_weight, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_vline(xintercept = 0, color = "red") +
  geom_smooth() +
  facet_wrap(~variable, scales = "free_y") +
  labs(x = "Log Biomass trend (g.m-1.y-1)", y = "Network trend (U.y-1)")
```

@@

```{r}
##Summary of group 
biomass_group %>%
  filter(group_type == "median") %>%
  ggplot(aes(x = bm)) +
  geom_histogram() +
  facet_wrap(bm_var~summary_type, scales = "free_x")
```
```{r, eval = FALSE}
group_results <- 
  rigal_biomass_coeff_dynamics %>%
  left_join(biomass_group, by = "station") %>% 
  filter(group_type == "median", bm_var == "bm_std")

@@

@@

bm_net_group %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
  geom_point() +
  scale_color_viridis() +
  #geom_smooth(method = "lm") +
  facet_wrap(~variable, scales = "free") +
  labs(title = "Group as mean biomass")

bm_net_group %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_errorbar(aes(
      xmin = bm_slope - bm_slope_strd_error,
      xmax = bm_slope + bm_slope_strd_error),
    alpha = .2
    ) +
  geom_errorbar(aes(
      ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error),
    alpha = .2
    ) +
  facet_wrap(~variable, scales = "free") +
  labs(title = "Group as mean biomass")

bm_net_group %>%
  filter(!is.na(protocol_type)) %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
  geom_point() +
  scale_color_viridis() +
  #geom_smooth(method = "lm") +
  facet_grid(variable~protocol_type, scales = "free") +
  labs(title = "Group as mean biomass")
```

@@

```{r, eval = TRUE}
loadd(model_bm, model_bm_vif)

model_bm_vif %>%
  ggplot(aes(y = vif, x = term)) +
  geom_hline(yintercept = 10) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(model_type~variable, scales = "free_x")
```

@@

```{r}
loadd(model_bm_by_protocol, model_bm_by_protocol_vif)

protocol_vec <- model_bm_by_protocol_vif$protocol_type %>% unique
p_vif_protocol <- map(protocol_vec, function (x) {
  model_bm_by_protocol_vif %>%
    filter(protocol_type == x) %>%
    ggplot(aes(y= vif, x = term)) +
    geom_hline(yintercept = 10) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = paste0("Protocol type: ", x)) +
    facet_grid(model_type~variable, scales = "free_y")
  })
p_vif_protocol[[1]]
p_vif_protocol[[2]]
```

```{r, eval = FALSE}
filter(model_bm_by_protocol_vif, model_type == "mod_bm_quad")
```

```{r}
bm_net_group %>%
  filter(variable == "connectance") %>%
  ggplot(aes(x = bm_slope, y = bm)) +
  geom_point()
```

@@

```{r, eval = TRUE}
loadd(model_bm_by_protocol_summary)
model_bm_by_protocol_summary %<>%
  filter(protocol_type == "complete")
```

```{r, eval = TRUE}
filter(model_bm_by_protocol_summary, model == "mod_inc_bm")[["resume"]]
filter(model_bm_by_protocol_summary, model == "mod_inc_bm")[["anova"]]

filter(model_bm_by_protocol_summary, model == "mod_bm_inc")[["resume"]]
filter(model_bm_by_protocol_summary, model == "mod_bm_inc")[["anova"]]

filter(model_bm_by_protocol_summary, model == "mod_bm_quad")[["resume"]]
filter(model_bm_by_protocol_summary, model == "mod_bm_quad")[["anova"]]

filter(model_bm_by_protocol_summary, model == "mod_bm_quad2")[["resume"]]
filter(model_bm_by_protocol_summary, model == "mod_bm_quad2")[["anova"]]
```

```{r, eval = TRUE}
pred <- model_bm_by_protocol_summary %>%
  filter(model == "mod_bm_inc") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]", "inc_f"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
plot_grid(plotlist = pred$plot, labels = pred$variable)
```

```{r}
pred <- model_bm_by_protocol_summary %>%
  filter(model == "mod_bm_quad2") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
plot_grid(plotlist = pred$plot_data, labels = pred$variable)
```

#### All protocol

```{r}
loadd(model_bm_summary)
```

```{r}
filter(model_bm_summary, model == "mod_inc_bm")[["resume"]]
filter(model_bm_summary, model == "mod_inc_bm")[["anova"]]

filter(model_bm_summary, model == "mod_bm_inc")[["resume"]]
filter(model_bm_summary, model == "mod_bm_inc")[["anova"]]

filter(model_bm_summary, model == "mod_bm_quad")[["resume"]]
filter(model_bm_summary, model == "mod_bm_quad")[["anova"]]

filter(model_bm_summary, model == "mod_bm_quad2")[["resume"]]
filter(model_bm_summary, model == "mod_bm_quad2")[["anova"]]
```

```{r}
pred_bm_quad2 <- model_bm_summary %>%
  filter(model == "mod_bm_quad2") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
plot_grid(plotlist = pred_bm_quad2$plot, labels = pred_bm_quad2$variable)
pred_bm_quad2_plot <- map2(model_bm$data, pred_bm_quad2$pred_df, plot_pred_data)

plot_grid(plotlist = pred_bm_quad2_plot, labels = pred_bm_quad2$variable)

pred_bm_quad <- model_bm_summary %>%
  filter(model == "mod_bm_quad") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )

pred_bm_quad_plot <- map2(model_bm$data, pred_bm_quad$pred_df, plot_pred_data)
plot_grid(plotlist = pred_bm_quad_plot, labels = pred_bm_quad2$variable)
```

#### Quadratic two

```{r}
#model_bm$data[[1]] %>%
  #ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
  #scale_fill_viridis() +
  #geom_point() +
  #geom_line(
    #data = pred_bm_quad2$pred_df[[1]] %>%
      #rename(bm_f = group, bm_slope = x, linear_slope = predicted),
    #aes(y = linear_slope, x = bm_slope, color = bm_f),
    #inherit.aes = FALSE)

test <- map2(model_bm$data, pred_bm_quad2$pred_df, function (.data, pred) {

  .data %>%
    ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
    scale_fill_viridis() +
    geom_point() +
    geom_line(
      data = pred %>%
	rename(bm_f = group, bm_slope = x, linear_slope = predicted),
      aes(y = linear_slope, x = bm_slope, color = bm_f),
      inherit.aes = FALSE)

    })
plot_grid(plotlist = test)
```

#### Quadratic one

```{r}
test <- map2(model_bm$data, pred_bm_quad$pred_df, function (.data, pred) {

  .data %>%
    ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
    scale_fill_viridis() +
    geom_point() +
    geom_line(
      data = pred %>%
	rename(bm_f = group, bm_slope = x, linear_slope = predicted),
      aes(y = linear_slope, x = bm_slope, color = bm_f),
      inherit.aes = FALSE)

    })
plot_grid(plotlist = test, labels = model_bm$variable)
```

@@

#### All protocol

```{r}
loadd(model_log_bm, model_log_bm_summary)
```

```{r}
filter(model_log_bm_summary, model == "mod_inc_bm")[["resume"]]
filter(model_log_bm_summary, model == "mod_inc_bm")[["anova"]]

filter(model_log_bm_summary, model == "mod_bm_inc")[["resume"]]
filter(model_log_bm_summary, model == "mod_bm_inc")[["anova"]]

filter(model_log_bm_summary, model == "mod_bm_quad")[["resume"]]
filter(model_log_bm_summary, model == "mod_bm_quad")[["resume"]] %>%
  map(., ~ .x$r.squared)
filter(model_log_bm_summary, model == "mod_bm_quad")[["anova"]]

filter(model_log_bm_summary, model == "mod_bm_quad2")[["resume"]]
filter(model_log_bm_summary, model == "mod_bm_quad2")[["resume"]] %>%
  map_dbl(., ~ .x$r.squared)

filter(model_log_bm_summary, model == "mod_bm_quad2")[["anova"]]

filter(model_log_bm_summary, model == "mod_log_bm_quad2")[["anova"]]
filter(model_log_bm_summary, model == "mod_log_bm_quad2")[["resume"]] %>%
  map_dbl(., ~ .x$r.squared)
```

#### Quadratic two

```{r}
pred_log_bm_quad2 <- model_log_bm_summary %>%
  filter(model == "mod_bm_quad2") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )

pred_log_bm_quad2_plot <- map2(model_log_bm$data, pred_log_bm_quad2$pred_df,
  plot_pred_data)
plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm$variable)
```

#### Quadratic one

```{r}
pred_log_bm_quad <- model_log_bm_summary %>%
  filter(model == "mod_bm_quad") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )

test <- map2(model_log_bm$data, pred_log_bm_quad$pred_df, plot_pred_data,
  std_error = TRUE)
plot_grid(plotlist = test, labels = model_log_bm$variable)
```

```{r}
loadd(log_bm_net_group, model_log_bm_vif)

model_log_bm_vif %>%
  ggplot(aes(y= vif, x = term)) +
  geom_hline(yintercept = 10) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(model_type~variable, scales = "free")
```

### By protocol

```{r}
loadd(model_log_bm_by_protocol_vif)

protocol_vec <- model_log_bm_by_protocol_vif$protocol_type %>% unique
p_vif_protocol <- map(protocol_vec, function (x) {
  model_log_bm_by_protocol_vif %>%
    filter(protocol_type == x) %>%
    ggplot(aes(y= vif, x = term)) +
    geom_hline(yintercept = 10) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = paste0("Protocol type: ", x)) +
    facet_grid(model_type~variable, scales = "free_y")
  })
p_vif_protocol[[1]]
p_vif_protocol[[2]]
```

```{r}
loadd(model_log_bm_by_protocol, model_log_bm_by_protocol_summary)
```

```{r}
filter(model_log_bm_by_protocol_summary, model == "mod_inc_log_bm")[["resume"]]
filter(model_log_bm_by_protocol_summary, model == "mod_inc_log_bm")[["anova"]]
```

```{r}
filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["resume"]]
filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["anova"]]

filter(model_log_bm_by_protocol_summary, model == "mod_bm_quad")[["resume"]]
filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["anova"]]
```

#### Quadratic two

```{r}
pred_log_bm_quad2 <- model_log_bm_by_protocol_summary %>%
  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
model_log_bm_by_protocol %<>% filter(protocol_type == "complete")

pred_log_bm_quad2_plot <- map2(model_log_bm_by_protocol$data, pred_log_bm_quad2$pred_df,
  plot_pred_data)
plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm$variable)
```

#### Quadratic one

```{r}
pred_log_bm_quad <- model_log_bm_by_protocol_summary %>%
  filter(model == "mod_bm_quad", protocol_type == "complete") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
model_log_bm_by_protocol %<>% filter(protocol_type == "complete")

pred_log_bm_quad_plot <- map2(model_log_bm$data, pred_log_bm_quad$pred_df, plot_pred_data,
  std_error = TRUE)
plot_grid(plotlist = pred_log_bm_quad_plot, labels = model_log_bm$variable)
```

```{r, eval = FALSE}
pred <- model_log_bm_by_protocol_summary %>%
  filter(model == "mod_log_bm_inc") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
  )
plot_grid(plotlist = pred$plot, labels = pred$variable)
```

```{r}
pred <- model_log_bm_by_protocol_summary %>%
  filter(model == "mod_log_bm_inc") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
  )
plot_grid(plotlist = pred$plot, labels = pred$variable)
```
